\cvsection{Education}
\begin{cventries}
  \cventry
    {PhD in Chemistry}
    {University of Bath(UBath)/Diamond Light Source(DLS)}
    {BATH/HARWELL-OXFORD, UK}
    {SEPT. 2015 - MAR. 2019}
    {
      \begin{cvitems}
        \item {Undertaking a PhD supervised by Prof. Karen Edler (UBath), Prof. Stephen Parker (UBath), Dr Andrew Smith (DLS) and Dr Jonathan Rawle (DLS).}
        \item {Developing computational methodologies and software to improve the analysis of small-angle scattering and reflectometry.}
        %\item {Developing computational methodologies and software to improve the analysis of small-angle scattering, reflectometry, and grazing incidence small-angle scattering.}
        \item {Applying classical atomistic and coarse-grained simulations to the study of soft matter systems.}
        \item {Implementing high-performance optimisation \& sampling algorithms to rationalise experimental scattering data.}
        %\item {Collaborative project co-funded by Diamond Light Source and the University of Bath.}
        %\item {Participated in many small-angle scattering and reflectometry experiments at Diamond Light Source and ISIS Neutron and Muon Source.}
        \item {Developing open educational resources to introduce classical simulation methods, including the pylj Python package and an introduction to classical simulation for users of small-angle scattering.}
      \end{cvitems}
    }
  \cventry
    {MChem in Materials Chemistry with a Year in Industry}
    {University of Edinburgh}
    {EDINBURGH, UK}
    {SEPT. 2010 - JUN. 2015}
    {
      \begin{cvitems}
        \item {Degree Classification: \textbf{First Class}.}
        \item {Spent one year learning practical soft matter chemistry/physics skills in industry at Cytec Industries.}
        \item {Masters research project: Collagen self-assembly using cryo-TEM.}
      \end{cvitems}
    }
\end{cventries}
