\cvsection{Key Outputs}
\begin{cventriesy}
  \cventryy
    {
      \begin{cvitemsy}
        \item {\textbf{A.~R. McCluskey}, T. Arnold, J.~F.~K. Cooper, \& T. Snow. \emph{Mach. Learn.: Sci. Technol.}, \textbf{1}(3), 035002, 2020 -- Independent research publication, making use of Bayesian model selection to improve understanding of the analysis of neutron reflectometry measurements}
    \vspace{1mm}
        \item {\textbf{A.~R. McCluskey}, A. J. Caruana, C. J. Kinane, A. J. Armstrong, T. Arnold, J. F. K. Cooper, D. L. Cortie, A. V. Hughes, J.-F. Moulin, A. R. J. Nelson, W. Potrzebowski, \& V. Starostin. \emph{J. Appl. Crystallogr.}, \textbf{56}(1), 12--17, 2023 -- First output from the open reflectometry standard organisation, offering guidence on the sharing of reflectometry analysis results}
    \vspace{1mm}
        \item {\textbf{A.~R. McCluskey}, J. Grant, A.~R. Symington, T. Snow, J. Doutch, B.~J. Morgan, S.~C. Parker, \& K.~J. Edler. \emph{J. Appl. Crystallogr.}, \textbf{52}(3), 665-668, 2019 -- An education-focused publication, discussing an open education resource to introduce users of diffraction techniques to classical simulation methods}
    \vspace{1mm}
        \item {\textbf{A.~R. McCluskey}, A. Sazonov, J.~F.~K. Cooper, S. Ward, P. Rozyczko, A. Pedersen, \& T. Holm Rod. EasyReflectometry, available at: \href{https://easyreflectometry.org}{easyreflectometry.org}, 2024 -- An open source graphical reflectometry analysis package, built to make reflectometry more accessible to new users}
    \vspace{1mm}
        \item {\textbf{A.~R. McCluskey*}, J. Grant, A.~J. Smith, J.~L. Rawle, D.~J. Barlow, M.~J. Lawrence, S.~C. Parker, \& K.~J. Edler*. \emph{J. Phys. Comm.}, \textbf{3}(7), 075001, 2019 -- Publication from PhD looking at the use of coarse-grained molecular dynamics simulations in the analysis of neutron reflectometry analysis}
    \end{cvitemsy}
    }
\end{cventriesy}
