\cvsection{Research Experience}
\begin{cventries}
  \cventry
    {Master's Project Student}
    {The Nudelman Group, University of Edinburgh}
    {EDINBURGH, UK}
    {SEPT. 2014 - APR. 2015}
    {
      \begin{cvitems}
        \item {Continued work from summer, investigating collagen self-assembly.}
        \item {Significant independent use of the cryogenic transmission electron microscope.}
        \item {Presented work at a national conference (First Joint Meeting of the Scottish Microscopy Group \& Microscopy Society of Ireland) as well as regularly at group meetings.}
      \end{cvitems}
    }
  \cventry
    {Summer Research Student}
	  {}
    {}
    {JUL. 2014 - SEPT. 2014}
    {
      \begin{cvitems}
        \item {Using cryogenic transmission electron microscopy to investigate self-assembly of collagen.}
        \item {Gained an appreciation of basic concepts from biochemistry and biophysics.}
        \item {Lead to work that continued during Master's project.}
      \end{cvitems}
    }
  \cventry
    {Temporary Research Intern}
    {Cytec Industries}
    {STAMFORD, USA}
    {JUN. 2013 - JUN. 2014}
    {
      \begin{cvitems}
        \item {Spent fourth year of Master's course in the Alumina group at Cytec Industries.}
        \item {Conducted research on the functionalisation and application of polyelectrolyte emulsions.}
        \item {Gained an understanding of common soft matter concepts, including colloid theory, and surfactant science.}
        \item {Developed skills related to statistical analysis, including significance testing and design of experiments.}
		\item {Presented work at group meeting and wrote monthly reports to keep group members updated on progress.}
      \end{cvitems}
    }
\end{cventries}
