\cvsection{Computational/Linguistic Skills}
\cvsubsection{Programming fluency \& Software familiarity}
	\begin{cvskills}
		\cvskill{Beginner}{FORTRAN90, C++, SQL, Docker}
		\cvskill{Experienced}{Julia, C, Java, OpenMP, MPI, Qt, HTML, CSS, TensorFlow, Keras, PyMC3, BinderHub, AWS, Google Cloud}
		\cvskill{Expert}{Python, Git, Jupyter-Framework, emcee, dynesty}
	\end{cvskills}
\cvsubsection{Software development}
    \begin{cvskillsy}
        \cvskill{\vspace{0.06cm}uravu}{An open-source Bayesian data analysis Python package. This gives access to powerful Bayesian inference libraries through a simple interface for model-dependent data analysis. Published in the Journal of Open Source Software.}
	\cvskill{kinisi}{A robust methodology for uncertainty quantification in \emph{in-silico} diffusion, implemented in an open-source Python package and available on Github.}
        \cvskill{islatu}{A open-source, documented package enabling reproducible and automated X-ray reflectometry reduction for data collected at the I07 beamline. Published in the Journal of Open Source Software.}
	\cvskill{pylj}{An open-source Python library to facilitate student interaction with classical atomistic simulation. It is designed to operate within the Jupyter notebook framework, making it easy to implement in the classroom or computer lab. Published in the Journal of Open-Source Education.}
	\end{cvskillsy}
\cvsubsection{Language fluency}
\begin{cvskillsx}
	\cvskill{Mother tongue}{English}
	\cvskill{CEFR-level B2}{Danish}
\end{cvskillsx}
