\cvsection{Teaching Experience}
\begin{cventries}
	\cventry
	{Visiting Lecturer}
	{University of Bath}
	{BATH, UK}
	{SEPT. 2019 - ONGOING}
	{
		\begin{cvitems}
			\item {Co-organisation and delivery of final year Chemistry course (CH40208), focused on introducing Python programming and applications of programming to computational chemistry}
			\item {Developed and delivered twenty-one hours of lecture-workshop hybrid classes to a cohort of seventy students}
		\end{cvitems}
	}
	\cventry
	{Introduction to Unix \& Programming Lecturer and Demonstrator}
	{}
	{}
	{FEB. 2018 - DEC. 2018}
	{
		\begin{cvitems}
			\item {Contributed a series of practical workshop designed to introduce PhD student from through-out the university of Unix and programming}
			\item {Included leading a ``Introduction of Python'' workshop, based on Software Carpentry materials}
		\end{cvitems}
	}
	\cventry
	{X-ray \& Neutron Techniques for Chemists Lecturer}
	{}
	{}
	{JAN. 2016 - MAY 2018}
	{
		\begin{cvitems}
			\item {Delivery of workshops devoted to the analysis of small-angle scattering and reflectometry as a component of a final year undergraduate course}
		\end{cvitems}
	}
	\cventry
	{Mathematics for Chemistry Lecturer}
	{}
	{}
	{SEPT. 2016 - MAR. 2017}
	{
		\begin{cvitems}
			\item {Delivery of workshops in fundamental mathematical concepts for chemists, ensuring that all chemistry first year students had a consistent mathematical background}
		\end{cvitems}
	}
	\cventry
	{Computational Laboratory Demonstrator}
	{}
	{}
	{JAN. 2016 - MAY 2018}
	{
		\begin{cvitems}
			\item {Helped in the running and development of first and second year undergraduate laboratory exercises, with a focus on the teaching of basic programming skills in Python and classical molecular dynamics}
		\end{cvitems}
	}
	\cventry
	{Physical Chemistry Tutor}
	{}
	{}
	{SEPT. 2015 - MAY 2018}
	{
		\begin{cvitems}
			\item {Running physical chemistry tutorials for first year natural sciences undergraduate students}
			\item {Pioneered the use of Jupyter Notebooks in tutorials to aid in the students understanding of the physical chemistry while introducing programming concepts}
		\end{cvitems}
	}
	\cventry
	{Contributor}
	{\href{https://pythoninchemistry.org}{Python in Chemistry}}
	{BATH, UK}
	{NOV. 2017 - PRESENT}
	{
		\begin{cvitems}
			\item {Lead developer of the open source ``An Introduction to Python for Chemists'' textbook; providing programming and data science skills to chemistry students}
			\item {Responsible for the development of an open educational resource focussed on the introduction of classical simulation to users of small-angle scattering}
			\item {Co-investigator for the pythoninchemistry Hackathon event, funded by the Royal Society of Chemistry Higher Education Group Kickstart Scheme}
		\end{cvitems}
	}
	\cventry
	{Lecturer}
	{ISIS Neutron Training Course}
	{HARWELL-OXFORD, UK}
	{MAR. 2017 - MAR. 2018}
	{
		\begin{cvitems}
			\item {Twice invited to lecture at the ISIS Neutron Training Course}
			\item {Developed and delivered a one hour lecture and interactive tutorial introducing classical molecular dynamics simulations and showing how they can be applied to neutron scattering}
		\end{cvitems}
	}
\end{cventries}
